### 2012-05-22 inst/examples/policycosts/exact_npv.Rmd
compute comperable intervals

`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="exact.npv/"-->
``` {r setup, include=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
````

@@

```{r }
dat <- data.table(dat)
dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]
````

>>>>

`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="exact.npv/" or`

``` {r setup, include=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
````

@@

```{r comparison}
dat <- data.table(dat)
int <- dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]$V1
dat$c2[int]
````
